Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-27 docs/paper.tex
Subject of this paper -> Subject of this work

	\subsection{Extending MAPF with matching}
	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this paper can be described.

>>>>

	\subsection{Extending MAPF with matching}
	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this work can be described.
